---
title: "aDDM"
author: "Jennifer March (jennifer.march@uni-hamburg.de)"
date: "3/26/2024"
output: html_document
---

# General Info

This script contains all the models tested in our manuscript (https://osf.io/preprints/psyarxiv/wvfnb). It requires JAGS. The script is structured s follows:

1. **Preparation:** loading libraries and load workspace
2. **Attentional DDM:** Function, Estimate aDDM, Test Parameters and some graphs (corresponds to aDDM)

# 1 Preparations
## 1.1 Load Libraries
```{r}
#clear working environment
rm(list=ls())

#clear all plots
#if(!is.null(dev.list())) dev.off()

#load required libraries
library(rtdists)
library(dfoptim)
library(readxl)
library(tidyr)
library(dplyr)
library(zoo)
library(tibble)
library(readr)
pacman::p_load(tidyverse, ez)
#parallel computing stuff
library(parallel)
library(doParallel)
library(foreach)
numCores <- detectCores()
registerDoParallel(cores=numCores)
#JAGS packages
library(R2jags) #should be put at the start but keep it here for the moment...
library(rtdists) #to be on the safe side when loading workspace (and not executing the first chunk above)
```

## 1.2 Create Theme for Plots
```{r}
myTheme <- theme(
  axis.line = element_line(colour = "black"), 
  panel.grid.major = element_blank(), 
  panel.grid.minor = element_blank(),  
  panel.border = element_blank(),   
  panel.background = element_blank(),
  text=element_text(size=16, colour = "black"), 
  axis.title.x = element_text(size=20, face="bold", colour = "black"), 
  axis.title.y = element_text( size=20, face="bold", colour = "black"),
  axis.text = element_text(size=16),
  strip.text =  element_text( size=16),
  strip.background = element_rect(fill = "white", colour = "black"),
  legend.background = element_rect(colour = "black"),
  legend.key = element_blank(),
  legend.key.size = unit(3, "lines"))
```

## 1.3 Load workspace 
```{r}
# load data
setwd("~/Desktop/WorkingProjects/JM_maaDDM/Hunger_across_domains/Modeling/Cloth")
load("../../data/datasets.RData")

#clear all plots
if(!is.null(dev.list())) dev.off()

# only include valid trials
data <- org_data_food_sated
validT <- which((is.na(data$fixProp1)==0)|(is.na(data$fixProp2)==0)|(is.na(data$fixProp3)==0)|(is.na(data$fixProp4)==0))
data <- data[validT, ]
N <- length(data$RT)
S <- length(unique(data$subject))

```


# 2 Attentional DDM 
## 2.1 Estimate maaDDM_noPhi with hierarchical Bayesian modeling (JAGS)
```{r}
# get data and initial values together and specify the model
ddmData <- list('N'=N,'S'=S,'P'=data$P_subj,'attribute1A'=data$upleft_val,'attribute1B'=data$upright_val,'attribute2A'=data$downleft_val,'attribute2B'=data$downright_val,'RT'=data$RT_right/1000,'fixProp1'=data$fixProp1,'fixProp2'=data$fixProp2,'fixProp3'=data$fixProp3,'fixProp4'=data$fixProp4)

#starting values
# nChains <- 8
nChains <- 3

#parallel computing apparently not possible
T1<-Sys.time()
addm_food <- jags.parallel(ddmData,inits = NULL,#jags.seed = sample(100:999,1),
parameters.to.save = c('mu_bound','sigma_bound','mu_ndt','sigma_ndt',
'mu_drift','sigma_drift','mu_weight1','sigma_weight1', 
'mu_theta','sigma_theta',
'bound','ndt','drift','weight1','theta'),

model.file = "BayesModel_maaDDM_noPhi.txt", 

working.directory = '../BayesModels_noHungry',

# n.chains = nChains, n.iter = 60000, n.burnin = 30000,n.thin = 12, 
n.chains = nChains, n.iter = 7000, n.burnin = 500,n.thin = 2, 
DIC = TRUE,jags.module = c("glm","dic","wiener"))

# Check duration of computing 
T2<-Sys.time() #T2-T1

# check convergence
ddmRhats <- addm_food$BUGSoutput$summary[,8] #check with max(Rhats), which should ideally be < 1.01 (1.05 would also be okay)
max(ddmRhats)
addm_food$BUGSoutput$DIC

save.image(file='addm_food.RData')

```

# 2.2 maaDDM
```{r}
# get data and initial values together and specify the model
maaDDM <- list('N'=N,'S'=S,'P'=data$P_subj,'attribute1A'=data$upleft_val,'attribute1B'=data$upright_val,'attribute2A'=data$downleft_val,'attribute2B'=data$downright_val,'RT'=data$RT_right/1000,'fixProp1'=data$fixProp1,'fixProp2'=data$fixProp2,'fixProp3'=data$fixProp3,'fixProp4'=data$fixProp4)

#starting values
# nChains <- 8
nChains <- 3

#parallel computing apparently not possible
T1<-Sys.time()
maaDDM_food <- jags.parallel(ddmData,inits = NULL,#jags.seed = sample(100:999,1),
parameters.to.save = c('mu_bound','sigma_bound','mu_ndt','sigma_ndt',
                                           'mu_drift','sigma_drift','mu_weight1','sigma_weight1',
                                           'mu_theta','sigma_theta','mu_phy','sigma_phy',
                                           'bound','ndt','drift','weight1','theta','phy'),

model.file = "BayesModel_maaDDM.txt", 

working.directory = '../BayesModels_noHungry',

# n.chains = nChains, n.iter = 60000, n.burnin = 30000,n.thin = 12, 
n.chains = nChains, n.iter = 7000, n.burnin = 500,n.thin = 2, 
DIC = TRUE,jags.module = c("glm","dic","wiener"))

# Check duration of computing 
T2<-Sys.time() #T2-T1

# check convergence and fit
ddmRhats <- maaDDM_food$BUGSoutput$summary[,8] #check with max(Rhats), which should ideally be < 1.01 (1.05 would also be okay)
max(ddmRhats)
maaDDM_food$BUGSoutput$DIC
#max R_hat = 1.032; DIC = 30546.33
save.image(file='maaDDM_food.RData')
```

# 2.3 maaDDM_2Phi
```{r}
#starting values
# nChains <- 8
nChains <- 3

#parallel computing apparently not possible
T1<-Sys.time()
maa2phiDDM_food <- jags.parallel(ddmData,inits = NULL,#jags.seed = sample(100:999,1),
parameters.to.save = c('mu_bound','sigma_bound','mu_ndt','sigma_ndt',
                                           'mu_drift','sigma_drift','mu_weight1','sigma_weight1',
                                           'mu_theta','sigma_theta','mu_phy','sigma_phy', 'mu_phy2','sigma_phy2', 
                                           'bound','ndt','drift','weight1','theta','phy', 'phy2'),

model.file = "BayesModel_maaDDM_2Phi.txt", 

working.directory = '../BayesModels_noHungry',

# n.chains = nChains, n.iter = 60000, n.burnin = 30000,n.thin = 12, 
n.chains = nChains, n.iter = 7000, n.burnin = 500,n.thin = 2, 
DIC = TRUE,jags.module = c("glm","dic","wiener"))

# Check duration of computing 
T2<-Sys.time() #T2-T1

# check convergence and fit
ddmRhats <- maa2phiDDM_food$BUGSoutput$summary[,8] #check with max(Rhats), which should ideally be < 1.01 (1.05 would also be okay)
max(ddmRhats)
maa2phiDDM_food$BUGSoutput$DIC
#max R_hat = 1.032; DIC = 30546.33
save.image(file='maa2phiDDM_food.RData')
```

# 3 Check Parameters (group posteriors)
```{r}
load(file='maa2phiDDM_food.RData')
#get group parameter estimates in transformed form 
ddm_results <- maa2phiDDM_food
boundSep <- log(1+exp(ddm_results$BUGSoutput$sims.list$mu_bound))
ndt <- log(1+exp(ddm_results$BUGSoutput$sims.list$mu_ndt))

weight1 <- pnorm(ddm_results$BUGSoutput$sims.list$mu_weight1)
drift <- log(1+exp(ddm_results$BUGSoutput$sims.list$mu_drift))

theta <- pnorm(ddm_results$BUGSoutput$sims.list$mu_theta)
phy <- pnorm(ddm_results$BUGSoutput$sims.list$mu_phy)
phy2 <- pnorm(ddm_results$BUGSoutput$sims.list$mu_phy2)
```

```{r}
# List of variable names, labels, and binwidths for each plot
est_parameters <- list(
  list(name = "weight1", label = "Taste Weight", binwidth = 1/100, maxY = 500),
  list(name = "drift", label = "Drift Scaling", binwidth = 1/170, maxY = 500),
  list(name = "boundSep", label = "Boundary Separation", binwidth = 1/30, maxY = 500),
  list(name = "ndt", label = "Non-Decision Time", binwidth = 1/150, maxY = 500),
  list(name = "theta", label = "Theta", binwidth = 1/850, maxY = 500),
  list(name = "phy", label = "phy", binwidth = 1/400, maxY = 250),
  list(name = "phy2", label = "phy2", binwidth = 1/400, maxY = 250)
)

# List to store plots
plot_list <- list()

# Loop over variables to create each plot
for (i in seq_along(est_parameters)) {
  param <- est_parameters[[i]]
  
  # Dynamically create data frame based on variable name
  param_data <- data.frame(value = get(param$name))
  
  # Create the plot
  plot_list[[i]] <- ggplot(param_data, aes(x = value)) +
    geom_histogram(binwidth = param$binwidth, fill = "cornflowerblue", alpha = 0.5, color = "black") +
    labs(x = param$label, y = "Frequency") +
    ylim(0, param$maxY) +
    myTheme
}

# Display plots (e.g., print(plot_list[[1]]), print(plot_list[[2]]), etc.)

```

```{r}
# difference between phy
phy_delta <- ddm_results$BUGSoutput$sims.list$mu_phy2-ddm_results$BUGSoutput$sims.list$mu_phy
data_delta_phy <- data.frame(phy_delta = phy_delta)
HDI_phy <- quantile(phy_delta,c(.025,.975))

# Plot using ggplot2
phy_plot<-ggplot(data_delta_phy, aes(x = phy_delta)) +
  geom_histogram(binwidth = 1/110, fill = "grey", alpha = 0.5, color = "black") +
  geom_vline(xintercept = 0, color = "red", size = 1.5) +
  geom_vline(xintercept = HDI_phy, color = "black", size = 1, linetype = "dashed") +
  ylim(0, 500)+
  labs(x = "Phy2>Phy1", y = "Frequency") +
  myTheme
# phy2 is significantly smaller than phy1
```

